\documentclass[helvetica]{seminar} 
\centerslidesfalse 
\input{xy}
\xyoption{all}
\usepackage{graphicx} 
\usepackage{slidesec} 
\usepackage{url} 

\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

% to fix problems making landscape seminar pdfs
% Letter...
\pdfpagewidth=11truein
\pdfpageheight=8.5truein
\pdfhorigin=1truein     % default value(?), but doesn't work without
\pdfvorigin=1truein     % default value(?), but doesn't work without
% A4
%\pdfpagewidth=297truemm % your milage may vary....
%\pdfpageheight=210truemm
%\pdfhorigin=1truein     % default value(?), but doesn't work without
%\pdfvorigin=1truein     % default value(?), but doesn't work without



\renewcommand{\familydefault}{\sfdefault}  
 
\input{seminar.bug} 
\input{seminar.bg2} % See the Seminar bugs list 
 
\slideframe{none} 
 
 
\usepackage{fancyhdr} 
 
% Headers and footers personalization using the `fancyhdr' package 
\fancyhf{} % Clear all fields 
\renewcommand{\headrulewidth}{0mm} 
\renewcommand{\footrulewidth}{0.1mm} 
 
\fancyfoot[L]{\tiny IETF 73} 
\fancyfoot[C]{\tiny DTLS 1.2}
\fancyfoot[R]{\tiny \theslide} 
 
 
% To center horizontally the headers and footers (see seminar.bug) 
\renewcommand{\headwidth}{\textwidth} 

% don't center vertically
\centerslidesfalse 
% To adjust the frame length to the header and footer ones 
\autoslidemarginstrue 
\pagestyle{fancy} 
 

\newcommand{\heading}[1]{% 
  \begin{center} 
    \large\bf 
    #1 
  \end{center} 
  \vspace{.4 in}} 
\begin{document}


        
\begin{slide}
\begin{center}
\LARGE{{\bf}DTLS 1.2 Status}\\

\vspace{.3 in}
\large{Eric Rescorla}\\
\large{RTFM, Inc.}\\
\large{\texttt{ekr@rtfm.com}}
\end{center}
\end{slide}


\begin{slide}
\heading{Current State}

\begin{itemize}
\item New draft: \url{draft-ietf-tls-rfc4347-bis-02.txt}
\item[]
\item Requirement to handle data from old epochs
\item Clarified Handling of data/handshake ordering during rehandshake
\item Clarified handling of sequence numbers and epochs
\item Clarified PMTU handling for stream-type transports
\item Clarified behavior of cookies with key changes
\item Are we done yet?
\end{itemize}
\end{slide}


\begin{slide}
\heading{Handling data from old epochs}

\begin{itemize}
\item Issue raised by Michael Tuexen
\item Some implementations reject data from old epochs during rehandshake
\begin{itemize}
\item This can create stalls
\end{itemize}
\item New requirement:
\end{itemize}
Until the handshake has
completed, implementations MUST accept packets from the old epoch.
\begin{quote}

\end{quote}
\end{slide}

\begin{slide}
\heading{Handling of sequence numbers}

\begin{itemize}
\item Raised by Robin Seggelman
\item Text isn't clear about sequence numbers and rehandshake
\item Intention: each epoch has its own seqno 
\begin{itemize}
\item Separate replay checks for each epoch
\end{itemize}
\item Changed text to clarify
\end{itemize}
\end{slide}


\begin{slide}
\heading{PMTU Handling}

\begin{itemize}
\item Issue raised by Michael Tuexen
\item Previous text said to assume stream transports had ``infinite PMTU''
\begin{itemize}
\item This doesn't make any sense
\end{itemize}
\item New text:
\end{itemize}

\begin{quote}
For DTLS over TCP or SCTP, which automatically fragment
and reassemble datagrams, there is no PMTU limitation.
However, the upper layer protocol MUST NOT write any
record that exceeds the maximum record size of $2^{14}$ bytes.
\end{quote}
\end{slide}



\begin{slide}
\heading{Data/handshake reordering}

\vspace{-.3 in}
\begin{itemize}
\item Issue raised by ???
\item What happens if handshake and data packets are reordered
\begin{itemize}
\item Can happen from the final agent to speak
\item New handshakes and rehandshakes are different
\end{itemize}
\item New text:
\end{itemize}

\begin{quote}
Note that in the special case of a rehandshake on an existing
association, it is safe to process a data packet immediately even if
the CSS or Finished has not yet been received provided that either
the rehandshake resumes the existing session or that it uses exactly
the same security parameters as the existing association.  In an
other case, the implementation MUST wait for the receipt of the
Finished to prevent downgrade attack.
\end{quote}
\end{slide}



\begin{slide}
\heading{Clarified cookie handling with key changes}

\begin{itemize}
\item Issue raised by ???
\item If the signing key changes, you can get multiple \textsf{HelloVerifyRequest}s
\item New text:
\end{itemize}

\begin{quote}
If a server receives a ClientHello with an invalid cookie, it SHOULD
treat it the same as a ClientHello with no cookie. This avoids
race/deadlock conditions if the client somehow gets a bad cookie
(e.g., because the server changes its cookie signing key). Note to
implementors: this may results in clients receiving multiple
HelloVerifyRequest messages with different cookies.  Clients SHOULD
handle this by sending a new HelloVerify in response to the new
HelloVerifyRequest.
\end{quote}

\end{slide}



\begin{slide}
\heading{Next Steps}

\begin{itemize}
\item Everything here was minor
\item And mostly clarifications of minor issues
\item Ready for WGLC?
\end{itemize}

\end{slide}


\end{document}