\documentclass[helvetica,fancybox,landscape]{seminar} 
\centerslidesfalse 
\usepackage{graphicx} 
\usepackage{slidesec} 
\usepackage{url} 
\input xy
\xyoption{all}
% Letter...
\pdfpagewidth=11truein
\pdfpageheight=8.5truein

\input{seminar.bug}
\input{seminar.bg2} % See the Seminar bugs list

\slideframe{none}
\renewcommand{\familydefault}{\sfdefault}  

\usepackage{fancyhdr}

% Headers and footers personalization using the `fancyhdr' package
\fancyhf{} % Clear all fields
\renewcommand{\headrulewidth}{0mm}
\renewcommand{\footrulewidth}{0.1mm}

\fancyfoot[L]{\tiny Eric Rescorla}
\fancyfoot[C]{\tiny TLS, IETF 67}
\fancyfoot[R]{\tiny \theslide}


% To center horizontally the headers and footers (see seminar.bug)
\renewcommand{\headwidth}{\textwidth}

% To adjust the frame length to the header and footer ones
\autoslidemarginstrue
\pagestyle{fancy}

\newcommand{\heading}[1]{% 
  \begin{center} 
    \large\bf 
    #1 
  \end{center} 
  \vspace{.4 in}} 

\begin{document}

\begin{slide}
\begin{center}
\LARGE{{\bf}TLS 1.2 Status}\\

\vspace{.3 in}
\large{Eric Rescorla}\\
\large{Network Resonance}\\
\large{\texttt{ekr@networkresonance.com}}

\end{center}
\end{slide}


\begin{slide}
\heading{DH Group/Exponent Checking}

\begin{itemize}
\item Basic issue: TLS uses arbitrary DH groups
\begin{itemize}
\item Chosen by the server
\item What if the server chooses an unsafe group?
\end{itemize}
\item Proposed solution
\begin{itemize}
\item Client SHOULD verify DH group correctness and modulus size
\begin{itemize}
\item Need a reference for how to check. Help!
\end{itemize}
\item Server MAY use a known group
\begin{itemize}
\item But no hint that this is a known group
\end{itemize}
\end{itemize}
\end{itemize}
\end{slide}



\begin{slide}
\heading{DigestInfo}

\begin{itemize}
\item We now use DigestInfo with RSA signatures
\item How is Parameters in AlgorithmIdentifier encoded?
\begin{itemize}
\item MUST be NULL
\item MUST be accepted as empty
\\\end{itemize}
\item Outcome of a decision in Prague:
\end{itemize}
\end{slide}


\begin{slide}
\heading{Cert Hash Types}

\begin{itemize}
\item Some comments on the list...
\item Generalized to signature hash types
\item Added a preference order
\end{itemize}

\end{slide}


\begin{slide}
\heading{Alerts}

\begin{itemize}
\item Any fatal alert MUST be sent
\begin{itemize}
\item Used to be optional
\end{itemize}
\item Error alerts sent before closure MUST be fatal
\item But alerts don't have to be sent
\end{itemize}

\begin{quote}
\tiny{
Whenever an implementation encounters a condition which is defined as
a fatal alert, it MUST send the appropriate alert prior to closing
the connection. In cases where an implementation chooses to send an
alert which MAY be a warning alert but intends to close the
connection immediately afterwards, it MUST send that alert at the
fatal alert level.

If an alert with a level of warning is sent and received, generally
the connection can continue normally.  If the receiving party decides
not to proceed with the connection (e.g., after having received a
no\_renegotiation alert that it is not willing to accept), it SHOULD
send a fatal alert to terminate the connection.
}
\end{quote}
\end{slide}


\begin{slide}
\heading{Signature Hash Agility (I)}

\begin{itemize}
\item Need a hash indicator
\item Also needs to be indicated in cert
\item Proposed new struct
\end{itemize}

{\tiny
\begin{verbatim}
       struct {
           select (SignatureAlgorithm) {
               case anonymous: struct { };
               case rsa:
                   HashType digest_algorithm;       // NEW
                   digitally-signed struct {
                       opaque hash[Hash.length];
                   };
               case dsa:
                   HashType digest_algorithm;       // NEW
                   digitally-signed struct {
                       opaque sha_hash[20];
                   };
               };
           };
       } Signature;
\end{verbatim}
}

\end{slide}


\begin{slide}
\heading{Signature Hash Agility (II)}

\begin{itemize}
\item Pasi suggests that \verb^digest_algorithm^ be an AlgorithmIdentifier
\begin{itemize}
\item Allows carrying parameters
\end{itemize}
\item This isn't the ordinary TLS style
\begin{itemize}
\item But we may need parameters
\end{itemize}
\item Proposal: pack into the signature if required
\end{itemize}

\end{slide}

\end{document}



